Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-04-11 article.rnw
Alter the post-process Data object so that it stores parameters using Parameters objects.

<<include=FALSE>>=
	source("r/input-data.R")
	source("r/post-process.R")
	source("r/brute-post-process.R")
	source("r/mantel-test.R")
	source("r/dist-matrix.R")
	source("r/coclassification-table.R")

>>>>

<<include=FALSE>>=
	source("r/parameters.R")
	source("r/input-data.R")
	source("r/post-process.R")
	source("r/brute-post-process.R")
	source("r/mantel-test.R")
	source("r/dist-matrix.R")
	source("r/coclassification-table.R")
